### 2017-03-14 thesis/misc/appendix2.tex
Draft thesis completed; now edit the whole thing - tmp commit

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/gatza_rma_meta_rank_vs_probit}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/gatza_rma_meta_rank_vs_probit}\\
		\includegraphics[width=0.32\linewidth,page=7]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=8]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=9]{appendix/gatza_rma_meta_rank_vs_probit}\\
		\includegraphics[width=0.32\linewidth,page=10]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=11]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=12]{appendix/gatza_rma_meta_rank_vs_probit}\\
		\caption[]{Scatter plots comparing the GT pathway metagenes ranked with probit and ranked based on number of samples in \gls{rma} normalised GT data. }
		\label{fig:appendix/rank_scatter}
	\end{figure}

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=7]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=8]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=9]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=10]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=11]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=12]{appendix/allmeta_rma_vs_mas}\\
		\caption[]{Scatter plots comparing the GT pathway metagenes derived from the transformation matrices (TM) in \gls{rma} or \gls{mas} normalised GT data set.
		All of the transformation matrices were generated in either the \gls{rma} or \gls{mas} normalised GT data set.
		}
		\label{fig:appendix/gt_meta_rma_mas}
	\end{figure}

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/gtrmastdrank}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/gtrmastdrank}\\
		\caption[]{Heatmaps showing the gene expression of the pathway associated genetic signatures, pathway metagenes, and the expression of the representative pathway gene in \gls{rma} normalised GT data set.
		For each pathway associated genetic signature, the gene expression pattern of the signature was plotted in the heatmap.
		The expression of the representative gene for the pathway signature (see \cref{tab:metagene_direction} in \cref{sub:metagene_direction}) was plotted seaparately as a bar above the pathway metagene scores.
		}
		\label{fig:appendix/gt_meta_rma_mas}
	\end{figure}

@@

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.7\linewidth]{results2/gatzares1}
		\caption[]{Heatmap showing the correlation of all of the GT pathway associated genetic signatures with one another.
		Figure adapted from the \citet{Gatza2010a} study.}
		\label{fig:gatza_paper_res}
	\end{figure}

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.65\linewidth,page=3]{appendix/gatza_meta_trans}
		\includegraphics[width=0.65\linewidth,page=7]{appendix/gatza_meta_trans}
		\caption[]{Heatmaps showing the correlation of all of the pathway metagenes with one another in \gls{rma} normalised CR, \gls{nzbc} and FM data sets.
		}
		\label{fig:appendix/gt_meta_rma_mas}
	\end{figure}

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/gtobrma}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/gtobrma}\\
		\includegraphics[width=0.32\linewidth,page=7]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=8]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=9]{appendix/gtobrma}\\
		\caption[]{Heatmaps showing the obesity metagenes from the CR data set with the gene expressions of the obesity associated genetic signatures in the \gls{rma} normalised GT data set.
		}
		\label{fig:appendix/ob_meta_dir_gt}
	\end{figure}

@@

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.24\linewidth,page=1]{results2/allmetacor_bar}
		\includegraphics[width=0.24\linewidth,page=2]{results2/allmetacor_bar}
		\includegraphics[width=0.24\linewidth,page=3]{results2/allmetacor_bar}
		\includegraphics[width=0.24\linewidth,page=4]{results2/allmetacor_bar}\\
		\caption[]{Visual comparison of the Spearman correlations of the \gls{svd}-derived and transformation matrix-derived pathway and obesity metagenes across different data sets}
		\label{fig:allmetacor_bar_appendix}
	\end{figure}

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.7\linewidth,page=3]{appendix/all_meta_trans}
		\caption[]{Heatmaps showing the correlation of all of the pathway and obesity metagenes with one another in \gls{rma} normalised CR, \gls{nzbc} and FM data sets.
		}
		\label{fig:appendix/gt_meta_rma_mas}
	\end{figure}

@@

		\caption[]{Description of the linear models used to predict the CrOl obesity metagene in \gls{nzbc} data set}

@@

		\caption[]{Description of the linear models used to predict the Res obesity metagene in \gls{nzbc} data set}

@@

		\caption[]{Description of the linear models used to predict the ResOl obesity metagene in \gls{nzbc} data set}

@@

		\caption[]{Description of the linear models used to predict the Ca obesity metagene in \gls{nzbc} data set}

@@

		\caption[]{Description of the linear models used to predict the CaOl obesity metagene in \gls{nzbc} data set}

@@

		\caption[]{Description of the linear models used to predict the CaRes obesity metagene in \gls{nzbc} data set}

@@

		\caption[]{Description of the linear models used to predict the CaResOl obesity metagene in \gls{nzbc} data set}

@@

		\caption[]{Description of the linear models used to predict the Or obesity metagene in \gls{nzbc} data set}

@@

		\caption[]{Description of the linear models used to predict the FM obesity metagene in \gls{nzbc} data set}

@@

	\begin{table}[htpb]
		\centering
		\caption[]{Description of the linear models used to predict the CrOl obesity metagene in \gls{nzbc} data set, using only the sample \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene scores}
		\label{tab:lm_pr_only_crol}
		\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.4484    & \bfseries \num{3.26d-06} \tnote{1} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.002084 & 0.5699  \\
                                                                               & \gls{pr}   & 0.4497    & \bfseries \num{3.36d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.09307  & 0.1440   \\
                                                                               & Overweight & -0.01989  & 0.7750   \\
                                                                               & \gls{pr}   & 0.4418    & \bfseries \num{4.32d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.008072  & 0.2060   \\
                                                                               & Obese      & -0.2048   & 0.06100   \\
                                                                               & Overweight & -0.06159  & 0.4230   \\
                                                                               & \gls{pr}   & 0.4294    & \bfseries \num{7.93d-06} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[]{Description of the linear models used to predict the Res obesity metagene in \gls{nzbc} data set, using only the sample \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene scores}
		\label{tab:lm_pr_only_res}
		\begin{threeparttable}
			\begin{tabular}{llr \bfseries S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.4926    & \bfseries \num{2.22d-07} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.001923 & 0.5904   \\
                                                                               & \gls{pr}   & 0.4938    & \bfseries \num{2.35d-07} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.08315  & 0.1790   \\
                                                                               & Overweight & 0.0001257 & 0.9990   \\
                                                                               & \gls{pr}   & 0.4862    & \bfseries \num{3.00d-07} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007716  & 0.2140   \\
                                                                               & Obese      & -0.1899   & 0.0740   \\
                                                                               & Overweight & -0.03974  & 0.5950   \\
                                                                               & \gls{pr}   & 0.4744    & \bfseries \num{5.78d-07} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[]{Description of the linear models used to predict the ResOl obesity metagene in \gls{nzbc} data set, using only the sample \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene scores}
		\label{tab:lm_pr_only_resol}
		\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.4581    & \bfseries \num{1.86d-06} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.001457 & 0.6897   \\
                                                                               & \gls{pr}   & 0.4590    & \bfseries \num{1.99d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.07789  & 0.2200   \\
                                                                               & Overweight & -0.01336  & 0.8480   \\
                                                                               & \gls{pr}   & 0.4526    & \bfseries \num{2.56d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007763  & 0.2230   \\
                                                                               & Obese      & -0.1853   & 0.0890   \\
                                                                               & Overweight & -0.05346  & 0.4860   \\
                                                                               & \gls{pr}   & 0.4407    & \bfseries \num{4.71d-06} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[]{Description of the linear models used to predict the Ca obesity metagene in \gls{nzbc} data set, using only the sample \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene scores}
		\label{tab:lm_pr_only_ca}
		\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.3850    & \bfseries \num{8.34d-05} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.001538 & 0.6848    \\
                                                                               & \gls{pr}   & 0.3859    & \bfseries \num{8.67d-05}  \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.07917  & 0.2274    \\
                                                                               & Overweight & 0.01954   & 0.7857    \\
                                                                               & \gls{pr}   & 0.3782    & \bfseries 0.0001060  \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.008992  & 0.1718    \\
                                                                               & Obese      & -0.2036   & 0.07034   \\
                                                                               & Overweight & -0.02692  & 0.7338    \\
                                                                               & \gls{pr}   & 0.3644    & \bfseries 0.0001830  \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[]{Description of the linear models used to predict the CaOl obesity metagene in \gls{nzbc} data set, using only the sample \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene scores}
		\label{tab:lm_pr_only_caol}
		\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.3425     & \bfseries 0.0005200  \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.0003869 & 0.9201    \\
                                                                               & \gls{pr}   & 0.3428     & \bfseries 0.0005530  \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.05462   & 0.4147    \\
                                                                               & Overweight & 0.03092    & 0.6742    \\
                                                                               & \gls{pr}   & 0.3373     & \bfseries 0.0006470  \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.008943   & 0.1842    \\
                                                                               & Obese      & -0.1784    & 0.1206    \\
                                                                               & Overweight & -0.01528   & 0.8504    \\
                                                                               & \gls{pr}   & 0.3236     & \bfseries 0.001060   \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

>>>>

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/gatza_rma_meta_rank_vs_probit}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/gatza_rma_meta_rank_vs_probit}\\
		\includegraphics[width=0.32\linewidth,page=7]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=8]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=9]{appendix/gatza_rma_meta_rank_vs_probit}\\
		\includegraphics[width=0.32\linewidth,page=10]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=11]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=12]{appendix/gatza_rma_meta_rank_vs_probit}\\
		\caption[Comparison of the ranking methods for the pathway metagenes in the \acrshort{rma}-normalised GT data]{Scatter plots comparing the GT pathway metagenes ranked with probit and ranked based on number of samples in \gls{rma} normalised GT data. }
		\label{fig:appendix/rank_scatter}
	\end{figure}

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=7]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=8]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=9]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=10]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=11]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=12]{appendix/allmeta_rma_vs_mas}\\
		\caption[Comparison of the normalisation methods used for the pathway metagene TM and the GT data]{Scatter plots comparing the GT pathway metagenes derived from the transformation matrices in \gls{rma}- or \gls{mas}-normalised GT data set.
		All of the transformation matrices were generated in either the \gls{rma} or \gls{mas} normalised GT data set.
		}
		\label{fig:appendix/gt_meta_rma_mas}
	\end{figure}

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/gtrmastdrank}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/gtrmastdrank}\\
		\caption[Directionality of the pathway metagenes in the GT data]{Heatmaps showing the gene expression of the pathway associated genetic signatures, pathway metagenes, and the expression of the representative pathway gene in \gls{rma}-normalised GT data set.
		For each pathway associated genetic signature, the gene expression pattern of the signature was plotted in the heatmap.
		The expression of the representative gene for the pathway signature (see \cref{tab:metagene_direction} in \cref{sub:metagene_direction}) was plotted seaparately as a bar above the pathway metagene scores.
		}
		\label{fig:appendix/gt_meta_rma_mas}
	\end{figure}

@@

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.7\linewidth]{results2/gatzares1}
		\caption[Original result presented in the \citet{Gatza2010a} study]{Heatmap showing the correlation of all of the GT pathway associated genetic signatures with one another.
		Figure adapted from the \citet{Gatza2010a} study.}
		\label{fig:gatza_paper_res}
	\end{figure}

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.65\linewidth,page=3]{appendix/gatza_meta_trans}
		\includegraphics[width=0.65\linewidth,page=7]{appendix/gatza_meta_trans}
		\caption[Heatmaps of the Pearson correlation of all the pathway metagenes in the \gls{rma}-normalised CR, \gls{nzbc} and FM data]{Heatmaps showing the correlation of all of the pathway metagenes with one another in \gls{rma} normalised CR, \gls{nzbc} and FM data sets.
		High and low correlation were represented as red and blue, respectively, where the colours were matched with the values on the scale shown in the top left histogram.}
		\label{fig:appendix/gt_meta_rma_mas}
	\end{figure}

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/gtobrma}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/gtobrma}\\
		\includegraphics[width=0.32\linewidth,page=7]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=8]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=9]{appendix/gtobrma}\\
		\caption[Heatmaps of all the obesity and the pathway metagenes in the CR, \gls{nzbc} and FM data]{Heatmaps showing the obesity metagenes from the CR data set with the gene expressions of the obesity associated genetic signatures in the \gls{rma} normalised GT data set.
		High and low correlation were represented as red and blue, respectively, where the colours were matched with the values on the scale shown in the top left histogram.}
		\label{fig:appendix/ob_meta_dir_gt}
	\end{figure}

@@

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.24\linewidth,page=1]{results2/allmetacor_bar}
		\includegraphics[width=0.24\linewidth,page=2]{results2/allmetacor_bar}
		\includegraphics[width=0.24\linewidth,page=3]{results2/allmetacor_bar}
		\includegraphics[width=0.24\linewidth,page=4]{results2/allmetacor_bar}\\
		\caption[Bar plots showing the Spearman correlation of the \gls{svd}- and TM-derived obesity and pathway metagenes across different data sets]{Visual comparison of the Spearman correlations of the \gls{svd}-derived and transformation matrix-derived pathway and obesity metagenes across different data sets}
		\label{fig:allmetacor_bar_appendix}
	\end{figure}

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.7\linewidth,page=3]{appendix/all_meta_trans}
		\caption[Heatmaps of the Pearson correlation of all the obesity and the pathway metagenes with one another in the \gls{rma}-normalised CR, \gls{nzbc} and FM data]{Heatmaps showing the correlation of all of the pathway and obesity metagenes with one another in the \gls{rma}-normalised CR, \gls{nzbc} and FM data sets.
		}
		\label{fig:appendix/gt_meta_rma_mas}
	\end{figure}

@@

		\caption{Description of the linear models constructed from the \gls{nzbc} data to predict the CrOl obesity metagene}

@@

		\caption{Description of the linear models constructed from the \gls{nzbc} data to predict the Res obesity metagene}

@@

		\caption{Description of the linear models constructed from the \gls{nzbc} data to predict the ResOl obesity metagene}

@@

		\caption{Description of the linear models constructed from the \gls{nzbc} data to predict the Ca obesity metagene}

@@

		\caption{Description of the linear models constructed from the \gls{nzbc} data to predict the CaOl obesity metagene}

@@

		\caption{Description of the linear models constructed from the \gls{nzbc} data to predict the CaRes obesity metagene}

@@

		\caption{Description of the linear models constructed from the \gls{nzbc} data to predict the CaResOl obesity metagene}

@@

		\caption{Description of the linear models constructed from the \gls{nzbc} data to predict the Or obesity metagene}

@@

		\caption{Description of the linear models constructed from the \gls{nzbc} data to predict the FM obesity metagene}

@@

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the CrOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the CrOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_crol}
		\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.4484    & \bfseries \num{3.26d-06} \tnote{1} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.002084 & 0.5699  \\
                                                                               & \gls{pr}   & 0.4497    & \bfseries \num{3.36d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.09307  & 0.1440   \\
                                                                               & Overweight & -0.01989  & 0.7750   \\
                                                                               & \gls{pr}   & 0.4418    & \bfseries \num{4.32d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.008072  & 0.2060   \\
                                                                               & Obese      & -0.2048   & 0.06100   \\
                                                                               & Overweight & -0.06159  & 0.4230   \\
                                                                               & \gls{pr}   & 0.4294    & \bfseries \num{7.93d-06} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the Res obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the Res obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_res}
		\begin{threeparttable}
			\begin{tabular}{llr \bfseries S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.4926    & \bfseries \num{2.22d-07} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.001923 & 0.5904   \\
                                                                               & \gls{pr}   & 0.4938    & \bfseries \num{2.35d-07} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.08315  & 0.1790   \\
                                                                               & Overweight & 0.0001257 & 0.9990   \\
                                                                               & \gls{pr}   & 0.4862    & \bfseries \num{3.00d-07} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007716  & 0.2140   \\
                                                                               & Obese      & -0.1899   & 0.0740   \\
                                                                               & Overweight & -0.03974  & 0.5950   \\
                                                                               & \gls{pr}   & 0.4744    & \bfseries \num{5.78d-07} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the ResOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the ResOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_resol}
		\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.4581    & \bfseries \num{1.86d-06} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.001457 & 0.6897   \\
                                                                               & \gls{pr}   & 0.4590    & \bfseries \num{1.99d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.07789  & 0.2200   \\
                                                                               & Overweight & -0.01336  & 0.8480   \\
                                                                               & \gls{pr}   & 0.4526    & \bfseries \num{2.56d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007763  & 0.2230   \\
                                                                               & Obese      & -0.1853   & 0.0890   \\
                                                                               & Overweight & -0.05346  & 0.4860   \\
                                                                               & \gls{pr}   & 0.4407    & \bfseries \num{4.71d-06} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the Ca obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the Ca obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_ca}
		\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.3850    & \bfseries \num{8.34d-05} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.001538 & 0.6848    \\
                                                                               & \gls{pr}   & 0.3859    & \bfseries \num{8.67d-05}  \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.07917  & 0.2274    \\
                                                                               & Overweight & 0.01954   & 0.7857    \\
                                                                               & \gls{pr}   & 0.3782    & \bfseries 0.0001060  \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.008992  & 0.1718    \\
                                                                               & Obese      & -0.2036   & 0.07034   \\
                                                                               & Overweight & -0.02692  & 0.7338    \\
                                                                               & \gls{pr}   & 0.3644    & \bfseries 0.0001830  \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}
